\begin{abstract}
The growing complexity of Cyber-physical Systems (CPSs) increasingly challenges existing methods and techniques. CPSs are often treated modularly to tackle both complexity and heterogeneity. A promising approach for verifying CPSs is to apply Functional Mock-up Interface (FMI) co-simulation techniques to obtain simulations of heterogeneous components in CPSs. However, the master algorithm for co-simulation may be livelock or deadlock. The architecture modelling of CPSs may also introduce an algebraic loop which is a feedback loop resulting in cyclic dependencies. To solve these problems, we propose a novel approach for model checking several properties of FMI co-simulation such as deadlock, liveness and reachability. We model the architecture of CPSs with SysML block diagrams, which captures the dependence of Functional Mock-up Units (FMUs) and the orchestration of the master algorithm. To verify the system, we encode FMUs components and model three various master algorithms with timed automata separately. With the help of encoding, we verify the master algorithms for co-simulation and detect algebraic loops in the architecture with the model checker UPPAAL. To illustrate the feasibility of our approach, the case study water tank is presented. The experiment results show that our approach facilitates model checking FMI co-simulation. The novelty of our work is that our approach supports to analyse co-simulation behavior of CPSs with model checking. 
\end{abstract}