 
%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for  contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{booktabs} % For formal tables
\usepackage[ruled]{algorithm2e} % For algorithms
\usepackage{multirow}
\usepackage{subfigure}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\geometry{a4paper,left=3.0cm,right=3.0cm
,top=3cm,bottom=3cm}
\usepackage{url}
\urldef{\mailsa}\path|{dhdu}@sei.ecnu.edu.cn|    
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}


% first the title is needed
\title{Model Checking FMI Co-simulation Using Timed Automata
\thanks{This work was supported by NSFC (Grant No.61472140, 61202104) and NSF of Shanghai (Grant No. 14ZR1412500).}}

% a short form should be given in case it is too long for the running head
%\titlerunning{Lecture Notes in Computer Science: Authors' Instructions}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Kaiqiang Jiang
\and Chunlin Guan\and Jiahui Wang\and Dehui Du*}
%
%\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Shanghai Key Laboratory of Trustworthy Computing, \\School of Computer Science and Software Engineering, East China Normal University, Shanghai, China\\
\mailsa}

%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

%\toctitle{Lecture Notes in Computer Science}
%\tocauthor{Authors' Instructions}
\maketitle


\begin{abstract}
Cyber-physical Systems(CPSs) focus on the coupling of cyber part viewed as distributed computation units and physical part covering the environment affecting the running of the system. CPSs are often treated modularly to tackle both complexity and heterogeneity. The verification of CPSs may be done modularly by Functional Mock-up Interface (FMI) co-simulation. However, the master algorithm for co-simulation may be livelock or deadlock. The architectural modelling of CPSs may introduce an algebraic loop which is a feedback loop resulting in instantaneous cyclic dependencies. To solve these problems, we propose a novel approach for model checking several properties of FMI co-simulation such as deadlock, liveness, reachability. 
We model the architecture of CPSs with SysML block diagrams, which captures the dependence of Functional Mock-up units (FMUs) and the orchestration of the master algorithm. Next, we encode FMU components and three various master algorithms with timed automata separately. Finally, we verify the correctness of the co-simulation and the absence of algebraic loops in the architecture with UPPAAL. To illustrate the feasibility of our approach, the case study water tank is presented. The results show that our approach helps model checking FMI co-simulation.
\keywords{Co-simulation, Master algorithm, Functional Mock-up Interface, Timed automata, Model checking}
\end{abstract}


\input{introduction}
\input{fmi}
\input{ma}
\input{sysml}
\input{ma&uppaal}
\input{relateworks}
\input{conclusion&ack}

\bibliographystyle{splncs03}

\bibliography{refcoma}
\end{document}
