\begin{abstract}
The growing complexity of Cyber-Physical Systems (CPS) increasingly challenges existing methods and techniques. The correctness of coordination between heterogeneous components of CPS is very important, which attracts more and more attentions. A promising approach for verifying coordination behaviour of CPS is simulation-based verification, which use Functional Mock-up Interface (FMI)-based co-simulation techniques to generate simulations of heterogeneous components in CPS. However, the master algorithm for co-simulation may be livelock or deadlock. Moreover, the architecture modeling of CPS may also introduce an algebraic loop which is a feedback loop resulting in cyclic dependencies. To solve these problems, we propose a novel approach for model checking several properties of coordination such as deadlock, liveness and reachability. This work aims at providing an effective approach to verify the coordination of heterogeneous components. We model the architecture of CPS with SysML block definition diagrams (BDDs), which captures the dependence of Functional Mock-up Units (FMUs) and the orchestration of the master algorithm. According to BDDs models, the coordination between components are implemented with the master algorithm. We encode FMUs components with Timed Automata (TA) to bridge the semantics gap between FMUs and TA. Besides, we model three various master algorithms with TA, which orchestrates the coordination between FMUs. With the help of the model checker UPPAAL, we can analyse the correctness of the master algorithms and detect whether there is an algebraic loop in the architecture. By this way, the coordination of CPS is verified with model checking.
To illustrate the feasibility of our approach, the case study water tank is presented. The experiment results show that our approach facilitates model checking coordination of CPS. The novelty of our work is that our approach supports to analyse coordination of CPS with TA. 
\end{abstract}