\begin{thebibliography}{zz}

\bibitem{built_env}
Hans-Arno Jacobsen, Randy H. Katz, Hartmut Schmeck, Christoph Goebel. Smart Buildings and Smart Grids[J]. Dagstuhl Reports, 2015, 5(2): 128-175.

\bibitem{smartbuilding}
张永坚, 周培祥, 高鹤. 智能建筑技术[M]. 中国水利水电出版社, 2007.

\bibitem{control_scheme}
Yao Jianguo, Giuseppe Tommaso Costanzo, Zhu Guchuan, Wen Bin. Power Admission Control With Predictive Thermal Management in Smart Buildings[J]. IEEE Transactions on Industrial Electronics, 2015, 62(4): 2642-2650.

\bibitem{thermal_model}
Jérôme Henri Kämpf, Darren Robinson. A simplified thermal model to support analysis of urban resource flows[J]. Energy and Buildings, 2007, 39(4): 445–453.

\bibitem{strategy_compare}
Domenico Gorni, María del Mar Castilla, José Domingo Álvarez, Antonio Visioli .A Comparison between Temperature Modeling Strategies in Smart Buildings[C]. Emerging Technologies \& Factory Automation(ETFA), 2015: 1-4.

\bibitem{performance_analysis}
Nathan Mendes, Gustavo H.C. Oliveira and Humberto X. de Araújo. Building Thermal Performance Analysis by Using matlab/simulink[C]. International Building Performance Simulation Association(IBPSA), 2001: 473-480.

\bibitem{energy1}
David A, Du Dehui, Larsen K, Mikucionis M, Skou A. An evaluation framework for energy aware buildings using statistical model checking[J]. SCIENCE CHINA Information Sciences, 2012, 55(12): 2694-2707.

\bibitem{energy2}
Chen Xiaohong, Gu Fan, Chen Mingsong, Du Dehui, Liu Jing, Sun Haiying. Evaluating Energy Consumption for Cyber-Physical Energy System: an Environment Ontology-Based Approach[C]. International Computer Software and Applications Conference, 2015: 5-14.

\bibitem{realtime}
Bouyer P, Fahrenberg U, Larsen K, Markey N. Quantitative analysis of real-time systems using priced timed automata[J]. Communications of the ACM (CACM), 2011, 54(9): 78-87.

\bibitem{uncertainty}
Chen Xiaoming, Li Xin, Sheldon X.-D. Tan. From Robust Chip to Smart Building: CAD Algorithms and Methodologies for Uncertainty Analysis of Building Performance[C]. International Conference on Computer-Aided Design(ICCAD), 2015: 457-464.

\bibitem{eval}
Du Dehui, Chen Mingsong, Liu Xiao, Yang Yun. A novel quantitative evaluation approach for software project schedules using statistical model checking[C]. International Conference on Software Engineering(ICSE), 2014: 476-479.

\bibitem{variation1}
Chen Mingsong, Yue Daian, Qin Xiaoke, Fu Xin, Mishra P. Variation-aware evaluation of MPSoC task allocation and scheduling strategies using statistical model checking[C]. Design, Automation, and Test in Europe(DATE), 2015: 199-204.

\bibitem{variation2}
Huang Saijie, Chen Mingsong, Liu Xiao, Du Dehui, Chen Xiaohong. Variation-Aware Resource Allocation Evaluation for Cloud Workflows using Statistical Model Checking[C]. International Conference on Big Data and Cloud Computing (BDCloud), 2014: 201-208.

\bibitem{pta1}
David A, Larsen K, Legay A, Mikucionis M, Poulsen D, Vliet J, Wang Zheng. Statistical Model Checking for Networks of Priced Timed Automata[C]. Formal Modeling and Analysis of Timed Systems(FORMATS), 2011: 80-96.

\bibitem{optim1}
Meysam Razmara, Guna R. Bharati, Mahdi Shahbakhti, Sumit Paudyal, Rush D. Robinett. Bidirectional Optimal Operation of Smart Building-to-Grid Systems. American Control Conference(ACC), 2015: 288-293.

\bibitem{optim2}
Zhao Hengyang, Daniel Quach, Wang Shujuan, Wang Hai, Chen Hai-Bao, Li Xin, Sheldon X.-D. Tan. Learning Based Compact Thermal Modeling for Energy-Efficient Smart Building Management[C]. International Conference on Computer-Aided Design(ICCAD), 2015: 450-456.

\bibitem{optim3}
Samuel Idowu, Saguna, Christer Åhlund, Olov Schelén. Forecasting Heat Load for Smart District Heating Systems: A Machine Learning Approach[C]. SmartGridComm, 2014: 554-559.

\bibitem{optim4}
Md. Sumon Shahriar, M. Sabbir Rahman. Urban Sensing and Smart Home Energy Optimisations: A Machine Learning Approach[C]. Internet of Things towards Applications(IoT-App), 2015: 19-22.

\bibitem{optim5}
Sakari Stenudd. A Model for Using Machine Learning in Smart Environments[C]. Grid and Pervasive Computing Workshops(GPC), 2011: 24-33.

\bibitem{ta1}
Alur R, Dill D. A theory of timed automata[J]. Theoretical Computer Science, 1994, 126(2): 183-235.

\bibitem{ta2}
Bengtsson J, Wang Yi: Timed Automata: Semantics, Algorithms and Tools[C]. Lectures on Concurrency and Petri Nets, 2003: 87-124.

\bibitem{pta2}
Behrmann G, Larsen K, Rasmussen J. Priced Timed Automata: Algorithms and Applications[C]. Formal Methods for Components and Objects, 2004: 162-182.

\bibitem{pta3}
Bulychev P, David A, Larsen K, Mikucionis M, Poulsen D, Legay A, Wang Zheng. UPPAAL-SMC: Statistical Model Checking for Priced Timed Automata[C]. Quantitative Aspects of Programming Languages and Systems, 2012: 1-16.

\bibitem{uppaal1}
Behrmann G, David A, Larsen K. A Tutorial on Uppaal[C]. Formal Methods for the Design of Real-Time Systems, 2004: 200-236.

\bibitem{model_checking}
Edmund M. Clarke, Orna Grumberg, Doron A. Peled. Model checking[M]. MIT Press, 2001.

\bibitem{smc1}
Axel Legay, Benoît Delahaye, Saddek Bensalem. Statistical Model Checking: An Overview[C]. Runtime Verification(RV), 2010: 122-135.

\bibitem{smc2}
Ananda Basu, Saddek Bensalem, Marius Bozga, Benoît Caillaud, Benoît Delahaye, Axel Legay. Statistical Abstraction and Model-Checking of Large Heterogeneous Systems[C]. Formal Techniques for Networked and Distributed Systems/Formal Methods for Open Object-Based Distributed Systems(FMOODS/FORTE), 2010: 32-46.

\bibitem{uppaal2}
UPPAAL. http://www.it.uu.se/research/group/darts/uppaal/about.shtml.

\bibitem{uppaal3}
Bengtsson J, Larsen K, Larsson F, Pettersson P, Wang Yi. UPPAAL - a Tool Suite for Automatic Verification of Real-Time Systems[C]. Hybrid Systems, 1995: 232-243.

\bibitem{smc3}
David A, Du Dehui, Larsen K, Legay A, Mikucionis M, Poulsen D, Sedwards S. Statistical Model Checking for Stochastic Hybrid Systems[J]. Hybrid Systems and Biology(HSB), 2012: 122-136.

\bibitem{smc4}
David A, Larsen K, Legay A, Mikucionis M, Wang Zheng. Time for Statistical Model Checking of Real-Time Systems[C]. Computer Aided Verification(CAV), 2011: 349-355.

\bibitem{thermal1}
Thermal System. http://lpsa.swarthmore.edu/Systems/Thermal/SysThermalIntro.html.

\bibitem{thermal2}
Deng Kun, Barooah P, Mehta P, Meyn S. Building Thermal Model Reduction via Aggregation of States[C]. American Control Conference, 2010: 5118-5123.

\bibitem{machine_learning1}
Machine learning. Wikipedia: https://en.wikipedia.org/wiki/Machine\_learning.

\bibitem{machine_learning2}
Stuart J. Russell, Peter Norvig. Artificial Intelligence - A Modern Approach (3. internat. ed.)[M]. Pearson Education, 2010.

\bibitem{ann}
I.A. Basheer, M. Hajmeer. Artificial neural networks: fundamentals, computing, design, and application[J]. Journal of Microbiological Methods, 2000, 43: 3–31.

\bibitem{nn}
Raúl Rojas. Neural Networks - A Systematic Introduction[M]. Springer, 1996.



\bibitem{cps1}
尹玲, 陈小红 ,刘静. 信息物理融合系统的时间需求一致性分析[J]. 软件学报, 2014, 25(2): 400-418.



\end{thebibliography}

